Understanding and Verifying the Shape of Stencil Computations

### 2017-03-28 oopsla17/lattice-model.tex
Take Point out of equational axioms
It is also not a useful proposition so take it out of there as well.

\begin{description}
  \item[Basic] \texttt{*} and \texttt{+} are both idempotent, commutative, and
    associative;
%
  \item[Subsumption] If $S$ and $R$ are regions with $S \preceq R$, then
    $S \texttt{+} R \equiv R$ and $S \texttt{*} R \equiv S$.
%
  \item[Dist] \texttt{*} distributed over \texttt{+} and dually
    \texttt{+} distributes over \texttt{*}, meaning if \textcap{R}, \textcap{S},
    and \textcap{T} are regions, then we have the following dual equivalences:
%
    \begin{align*}
      \texttt{\textcap{R}*(\textcap{S}+\textcap{T})} & \equiv
        \texttt{(\textcap{R}*\textcap{S})+(\textcap{R}*\textcap{T})} &
      \texttt{\textcap{R}+(\textcap{S}*\textcap{T})} & \equiv
        \texttt{(\textcap{R}+\textcap{S})*(\textcap{R}+\textcap{T})}
    \end{align*}
%
  \item[Overlapping pointed] If \textcap{R} is one of \texttt{forward},
    \texttt{backward}, or \texttt{centered}, then we have
    $\stencil{\textcap{R}}{$n$}{$k$}{\texttt{nonpointed}} \;\texttt{+}\;
     \stencil[s]{p}{$n$}{}{} \equiv
     \stencil{\textcap{R}}{$n$}{$k$}{}$.
%
  \item[Centered] The region constants \texttt{forward} and \texttt{backward}
    are two halves of \texttt{centered} specifications:
%
    \begin{equation*}
      \stencil[s]{c}{$n$}{$k$}{\textcap{p1}} \equiv
        \stencil[s]{f}{$n$}{$k$}{\textcap{p2}} \texttt{+}
        \stencil[s]{b}{$n$}{$k$}{\textcap{p3}}
    \end{equation*}
%
    Here \textcap{p1} is \texttt{nonpointed} if both \textcap{p2} and
    \textcap{p3} are \texttt{nonpointed} and \texttt{pointed} otherwise.
%
  \item[Point] Let \textcap{R} and \textcap{S} be region constants with two
    variants a superscript \textit{f} to mean nonpointed and \textit{t} to mean
    pointed and \textcap{dr} \& \textcap{ds} be the dimensions \textcap{R} and
    \textcap{S} acts on. Then we have the following dual equivalences:
%
    \begin{align*}
      (\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{f}})
      \;\texttt{+}\;
      (\textcap{R}^{\textit{f}} \texttt{*} \textcap{S}^{\textit{t}})
      \;\texttt{+}\;
      \stencil[s]{p}{\textit{dr}}{}{}*\stencil[s]{p}{\textit{ds}}{}{} & =
        \textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}} \\
%
      (\textcap{R}^{\textit{t}} \texttt{+} \textcap{S}^{\textit{f}}) \texttt{*}
      (\textcap{R}^{\textit{f}} \texttt{+} \textcap{S}^{\textit{t}}) & =
        \textcap{R}^{\textit{f}} \texttt{+} \textcap{S}^{\textit{f}}
        \;\texttt{+}\;
        \stencil[s]{p}{\textit{dr}}{}{}*\stencil[s]{p}{\textit{ds}}{}{}
    \end{align*}
\end{description}

@@

      Using \Cref{lem:vector-union}, it is sufficient to show
      $ \interv{-k}{k}{p} \;\cup\; \interv{0}{0}{\textsf{true}} =
        \interv{-k}{k}{\textsf{true}} $ holds. This immediately follows from
      \Cref{lem:zinf-identities}.
%
    \item[Centered] Let $\interp{\textcap{p1}}$, $\interp{\textcap{p2}}$, and
      $\interp{\textcap{p3}}$ be $p1$, $p2$, and $p3$ respectively. We
      know that $p1$ is $p2 \vee p3$ from (\textbf{Centered}) detinition. Then
      we get the following interpretation for region constants involved in the
      equivalence:
%
      \begin{align*}
        \interp{\stencil{c}{$k$}{$n$}{$p1$}}_N
          &= \vecgen{N}{n}{\interv{-k}{k}{p2 \vee p3}} \\
%
        \interp{\stencil{f}{$k$}{$n$}{$p2$}}_N
          &= \vecgen{N}{n}{\interv{0}{k}{p2} }\\
%
        \interp{\stencil{b}{$k$}{$n$}{$p3$}}_N
          &= \vecgen{N}{n}{\interv{0}{k}{p3}}
      \end{align*}
%
      Using \Cref{lem:vector-union}, it is sufficient to show $\interv{-k}{k}{p2
      \vee p3} = \interv{0}{k}{p2} \cup \interv{-k}{0}{p3}$ holds. This
      immediately follows from \Cref{lem:zinf-identities}.

    \item[Point] We will prove the first equivalence and then use that to prove
      the second.
%
      Let $\interp{\textcap{R}^{\textnormal{\textit{p}}}}_N$ and
      $\interp{\textcap{S}^{\textnormal{\textit{p'}}}}_N$ be
      $\vecgen{N}{k}{\interv{a}{b}{p}}$ and $\vecgen{N}{l}{\interv{c}{d}{p'}}$
      respectively for some $a$ and $c$ less than or equal to 0, for some $c$
      and $d$ greater than or equal to 0, for some indices $k$ and $l$ be
      $\interp{\textcap{dr}}$ and $\interp{\textcap{ds}}$, which are not
      necessarily distinct and $p$ and $p'$ are \textsf{true} if pointed and
      \textsf{false} otherwise.
%
      \begin{align*}
        \hspace{2em&\hspace{-2em}}
        \interp
          {{(\textcap{R}^{\textit{t}} * \textcap{S}^{\textit{f}})}
           \;\texttt{+}\;
           {(\textcap{R}^{\textit{f}} * \textcap{S}^{\textit{t}})}
           \;\texttt{+}\;
           \texttt{pointed(dim=\textcap{dr})*pointed(dim=\textcap{ds})}}_N \\
        & = {(\interp{\textcap{R}^{\textit{t}}}_N \cap
              \interp{\textcap{S}^{\textit{f}}}_N)} \cup
            {(\interp{\textcap{R}^{\textit{f}}}_N \cap
              \interp{\textcap{S}^{\textit{t}}}_N)} \;\cup \\
        & \quad\,\, {(\vecgen{N}{\interp{ds}}{\interv{0}{0}{\textsf{true}}}
                      \;\cup\;
                      \vecgen{N}{\interp{dr}}{\interv{0}{0}{\textsf{true}}})} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
            \wedge {(c \leq x_l \leq d \wedge x_l \neq 0)} \} \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge {(a \leq x_k \leq b \wedge x_k \neq 0)}
            \wedge c \leq x_l \leq d \} \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge (x_k = 0 \wedge x_l = 0) \} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
          \wedge c \leq x_l \leq d \wedge {(x_k \neq 0 \vee x_l \neq 0)} \}
          \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge (x_k = 0 \wedge x_l = 0) \} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
            \wedge c \leq x_l \leq d \} \\
        & = \interp{\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}}}_N
      \end{align*}
%
      Now we prove the second equivalence:
      \begin{align*}
        \hspace{2em}&\hspace{-2em} \interp{%
            (\textcap{R}^{\textit{t}} \texttt{+} \textcap{S}^{\textit{f}})
            \texttt{*}
            (\textcap{R}^{\textit{f}} \texttt{+} \textcap{S}^{\textit{t}})
          }_N \\
        &= \interp{%
             (\textcap{R}^{\textit{t}} \texttt{*} \textcap{R}^{\textit{f}})
             \texttt{+}
             (\textcap{S}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{f}})
             \texttt{+}
             (\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}})
             \texttt{+}
             (\textcap{R}^{\textit{f}} \texttt{*} \textcap{S}^{\textit{f}})
           }_N \\
        &= \interp{%
             \textcap{R}^{\textit{f}}
             \texttt{+}
             \textcap{S}^{\textit{f}}
             \texttt{+}
             (\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}})
           }_N \\
        &= \interp
             {\textcap{R}^{\textit{f}}
              \texttt{+}
              \textcap{S}^{\textit{f}}
              \texttt{+}
              {(\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{f}})}
               \;\texttt{+}\;
               {(\textcap{R}^{\textit{f}} \texttt{*} \textcap{S}^{\textit{t}})}
               \;\texttt{+}\;
               \texttt{pointed(dim=\textcap{dr})*pointed(dim=\textcap{ds})}}_N \\
        &= \interp{\textcap{R}^{\textit{f}} \texttt{+} \textcap{S}^{\textit{f}}
                   \;\texttt{+}\;
                   \texttt{pointed(dim=\textcap{dr})*pointed(dim=\textcap{ds})}}_N
      \end{align*}
  \end{description}
\end{proof}

>>>>

\begin{description}
  \item[Basic] \texttt{*} and \texttt{+} are both idempotent, commutative, and
    associative;
%
  \item[Subsumption] If $S$ and $R$ are regions with $S \preceq R$, then
    $S \texttt{+} R \equiv R$ and $S \texttt{*} R \equiv S$.
%
  \item[Dist] \texttt{*} distributed over \texttt{+} and dually
    \texttt{+} distributes over \texttt{*}, meaning if \textcap{R}, \textcap{S},
    and \textcap{T} are regions, then we have the following dual equivalences:
%
    \begin{align*}
      \texttt{\textcap{R}*(\textcap{S}+\textcap{T})} & \equiv
        \texttt{(\textcap{R}*\textcap{S})+(\textcap{R}*\textcap{T})} &
      \texttt{\textcap{R}+(\textcap{S}*\textcap{T})} & \equiv
        \texttt{(\textcap{R}+\textcap{S})*(\textcap{R}+\textcap{T})}
    \end{align*}
%
  \item[Overlapping pointed] If \textcap{R} is one of \texttt{forward},
    \texttt{backward}, or \texttt{centered}, then we have
    $\stencil{\textcap{R}}{$n$}{$k$}{\texttt{nonpointed}} \;\texttt{+}\;
     \stencil[s]{p}{$n$}{}{} \equiv
     \stencil{\textcap{R}}{$n$}{$k$}{}$.
%
  \item[Centered] The region constants \texttt{forward} and \texttt{backward}
    are two halves of \texttt{centered} specifications:
%
    \begin{equation*}
      \stencil[s]{c}{$n$}{$k$}{\textcap{p1}} \equiv
        \stencil[s]{f}{$n$}{$k$}{\textcap{p2}} \texttt{+}
        \stencil[s]{b}{$n$}{$k$}{\textcap{p3}}
    \end{equation*}
%
    Here \textcap{p1} is \texttt{nonpointed} if both \textcap{p2} and
    \textcap{p3} are \texttt{nonpointed} and \texttt{pointed} otherwise.
\end{description}

@@

      Using \Cref{lem:vector-union}, it is sufficient to show
      $ \interv{-k}{k}{p} \;\cup\; \interv{0}{0}{\textsf{true}} =
        \interv{-k}{k}{\textsf{true}} $ holds. This immediately follows from
      \Cref{lem:zinf-identities}.
%
    \item[Centered] Let $\interp{\textcap{p1}}$, $\interp{\textcap{p2}}$, and
      $\interp{\textcap{p3}}$ be $p1$, $p2$, and $p3$ respectively. We
      know that $p1$ is $p2 \vee p3$ from (\textbf{Centered}) detinition. Then
      we get the following interpretation for region constants involved in the
      equivalence:
%
      \begin{align*}
        \interp{\stencil{c}{$k$}{$n$}{$p1$}}_N
          &= \vecgen{N}{n}{\interv{-k}{k}{p2 \vee p3}} \\
%
        \interp{\stencil{f}{$k$}{$n$}{$p2$}}_N
          &= \vecgen{N}{n}{\interv{0}{k}{p2} }\\
%
        \interp{\stencil{b}{$k$}{$n$}{$p3$}}_N
          &= \vecgen{N}{n}{\interv{0}{k}{p3}}
      \end{align*}
%
      Using \Cref{lem:vector-union}, it is sufficient to show $\interv{-k}{k}{p2
      \vee p3} = \interv{0}{k}{p2} \cup \interv{-k}{0}{p3}$ holds. This
      immediately follows from \Cref{lem:zinf-identities}.
  \end{description}
\end{proof}
